\documentclass{article}[18pt]
\usepackage{../../../../format}
\lhead{NVC}


\begin{document}
\begin{center}
\underline{\huge Video}
\end{center}
\section{Problem}
Amateur photographers have great difficulty finding clients, as larger businesses are taking all of their customers, however many clients aren't looking for photos of the quality provided by professional photographers and would settle for slightly worse photos at a much better price. However, in this market there is nothing to connect these two groups.  
\section{Solution}
We provide a solution to this, providing a platform for amateur photographers to search for clients. This is in the form of an app, which sorts all the connection and payment in return for a small fee. This is one of the first apps of its kind and will allow us to succeed. 
\section{Traction}
We will gain traction through advertising, starting by targeting university societies and events as clients. This is in a setting we are familiar with and will allow us to make good connections. We will also be able to find university student photographers as students are always looking for more ways to make money and with the highly skilled cohort at Durham we are sure we will be able to find many high quality photographers.
\section{Management}
Our company will start small and so have a very simple management structure with each of the 3 of us with equal responsibility, but each working on different aspects of the company according to our skillsets. Possible future expansion of this company would have us manage workers, such as programmers or marketing experts. We may decide in the future to appoint one person as CEO of the company, but while the company is still small we believe it better to remain agile and have each person operating independently, this will allow us to move faster and have more dynamic ideas as each person can fully utilise their unique talents.
\section{Advisory Board}
Our advisory board will be generated from the university societies, such as Entrepreneurs Durham. These are students who have expertise in a variety of business areas and will be able to provide us with the guidance we need as we are starting up.\\
This advisory board will be useful in providing us with people with a greater depth of experience, alongside professional connections. This will allow us to grow faster than we could otherwise, giving us a competitive advantage to any copycat apps, which should hopefully allow us to be the market leader in this area.





\end{document}